### 2009-11-29 doc/manuals/janitor/tex_concept/concept.tex
Merged concept.tex

 The main language for the implementation of the functionality of the
 dRTE's functionality is Perl. And it is solely required (exceptions are the
 integration with the Grid Manager and the Web server) for the Janitor.
 The language was perceived a side-issue, the complexity of the data
 expected was of major concern.

@@

 \begin{landscape}
\begin{figure}[!h]
\vspace{4cm}
 \begin{center} 
%    \resizebox{24cm}{!}{\input{images/dependencies}}
    \includegraphics[width=24cm]{images/dependencies.png}
    \mycaption{Modules of the Janitor and their dependencies}{}
 \end{center} 
\vfill
 \label{fig:janitorDependencies} 
\end{figure}
 \end{landscape}

@@

\subsection{States of runtime environments}

@@

These states are specific for every compute element (CE) and communicated
between the Janitor and the Execution Service. Table~\ref{tab:states} shows all
possible states, while Figure~\ref{fig:RE_states}
displays the transitions between the states that a Runtime Environment may
be in during its life time at a particular CE. \task{?at a particular CE?}

@@

The Janitor has two states for jobs: \texttt{PREPARED} and \texttt{INITIALIZED}. After a job has been succesfully registered 
in the Janitor, its state will be set to \texttt{PREPARED}. Invalid jobs are not cached. 
After the Janitor is requested to deploy the runtime environment, the state of the job will change to \texttt{INITIALIZED}. If 
an unforeseen exception occures during that process, the Janitor will drop the job from its database and set the affected runtime
environments to the state \texttt{FAILED}.

@@

\newenvironment{note}
{\rule{1ex}{1ex}\hspace{\stretch{1}}}
{\hspace{\stretch{1}}\rule{1ex}{1ex}\\}
\begin{note}
The integration into AREX is not completed yet!
\end{note}
\begin{note}
Thus, there will be bigger changes here in this section\dots
\end{note}

\begin{figure}[!h]
  \begin{center}
    \includegraphics[width=5cm]{images/arex-stages.pdf}
    \mycaption{}{}
    \label{fig:RE_states}
  \end{center}
\end{figure}

\begin{figure}[!h]
  \begin{center}
    \includegraphics[width=12cm]{images/janitor_integration_2nd_edition.pdf}
    \mycaption{}{}
    \label{fig:RE_states}
  \end{center}
\end{figure}

@@

Security is a major concern for grid systems. Any additional feature
and especially an automatic software
installation inheritently introduces security threats. This section
addresses those and describes the available solutions to limit
security risks.

In the current installation, every user authorised to execute a job is
also authorised to install a REs. Restrictions are
only imposed on the set of dynamic REs that are available for installation.
Restrictions are imposed by the site admininistrators on the descriptions
that are given by the Catalog that is offering the package. These
descriptions may explicitly mention dynamic REs' names, e.g. a regular expression on
these, or refer to tags of packages that categorise these. However,
the core of these controls lies with the maintainers of the Catalog,
who needs to be trusted.

@@

\begin{itemize}
\item Dynamic REs are not distinguished between {\em installed} and
  {\em installable} in the information system.
\item No status information is given at the time a dynamic RE is installed.
\end{itemize}

@@

The worst case scenario would be the installation of a RE
that overwrites system files. With the current implementation, which is
based solely on tar files, this is barely possible, unless such is
performed by the install scripts that accompany the tar files. However,
hereto the installation would have to be performed by a user with system
priviledges, for which there is no technical requirement.

>>>>

The main language for the implementation of the functionality of the
dRTEs' functionality is Perl. And it is solely required (exceptions
are the integration with the Grid Manager and the Web service) for the
Janitor.
The language was perceived a side-issue, the complexity of the data
expected was of major concern. This led to the choice of RDF with its
intrinsic query engine and Perl offering access to the Redland library.

@@

\begin{landscape}
 \begin{figure}[!h]
 \vspace{4cm}
 \begin{center} 
 %\resizebox{24cm}{!}{\input{images/dependencies}}
 %\includegraphics[width=24cm]{images/dependencies.png}
 \includegraphics[width=24cm]{images/dependencies.pdf}
 \mycaption{Modules of the Janitor and their dependencies}{}
 \end{center} 
 \vfill
 \label{fig:janitorDependencies} 
 \end{figure}
\end{landscape}

@@

\subsection{States of Runtime Environments}

@@

These states are specific for every compute element (CE) and communicated
between the Janitor and the Execution Service. Table~\ref{tab:states}
shows all
possible states, while Figure~\ref{fig:RE_states}
displays the transitions between the states that a Runtime Environment may
be in during its life time at a particular CE.

@@

The Janitor has two states for jobs: \texttt{PREPARED} and
\texttt{INITIALIZED}. After a job has been succesfully registered with
the Janitor, its state will be set to \texttt{PREPARED}. Invalid jobs
are not cached.  After the Janitor is requested to deploy the runtime
environment, the state of the job will change to \texttt{INITIALIZED}. If
an unforeseen exception occures during that process, The Janitor will drop
the job from its database and set the affected runtime environments to
the state \texttt{FAILED}.

@@

\newenvironment{note}
{\rule{1ex}{1ex}\hspace{\stretch{1}}}
{\hspace{\stretch{1}}\rule{1ex}{1ex}\\}

\begin{figure}[!h]
  \begin{center}
    \includegraphics[width=5cm]{images/arex-stages.pdf}
    \mycaption{}{}
    \label{fig:arex_states}
  \end{center}
\end{figure}

\begin{figure}[!h]
  \begin{center}
    \includegraphics[width=12cm]{images/janitor_integration_2nd_edition.pdf}
    \mycaption{}{}
    \label{fig:janitor_integration_2}
  \end{center}
\end{figure}

@@

Security is a major concern for grid systems. Any additional feature
and especially an automated software
installation inheritently introduces security threats. This section
addresses those and describes the available solutions to limit
security risks.

In the current installation, every user authorised to execute a job is
also authorised to install a REs. Restrictions are
only imposed on the set of dynamic RTEs that are available for installation.
Restrictions are imposed by the site admininistrators on the descriptions
that are given by the Catalog that is offering the package. These
descriptions may explicitly mention dynamic REs' names, e.g. a regular expression on
these, or refer to tags of packages that categorise these. However,
the core of these controls lies with the maintainers of the Catalog,
who needs to be trusted.

@@

\begin{itemize}
\item Dynamic RTEs are not distinguished between {\em installed} and
  {\em installable} in the information system.
\item No status information is given at the time a dynamic RE is installed.
\end{itemize}

@@

The worst case scenario would be the installation of a RE
that overwrites system files. With the current implementation, which is
based solely on tar files, this is barely possible, unless such is
performed by the install scripts that accompany the tar files.
\task{Clarify root vs non-root execution of Janitor.}
%However,
%hereto the installation would have to be performed by a user with system
%priviledges, for which there is no technical requirement.
